The \kepler Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants

### 2018-08-27 paper/ms.tex
rearrange slightly

% This author list is not final! If you think you should be in a different position please do not hesitate to say so.
\author[B. J. S. Pope et al.]{Benjamin J. S. Pope,$^{1,2,3}$\thanks{E-mail: benjamin.pope@nyu.edu}
Guy R. Davies,$^{4,5}$
Keith Hawkins,$^{6,7}$
Timothy R. White,$^{5,8}$\newauthor
Daniel Huber,$^{9,10,11}$
Ashley Chontos,$^{9}$
Victor Silva Aguirre,$^{5}$
Victoria Antoci,$^{5}$\newauthor
Suzanne Aigrain,$^{3}$ 
Timothy R. Bedding,$^{10,5}$
Jie Yu,$^{10,5}$ 
Amalie Stokholm,$^{5}$\newauthor
Timothy van Reeth,$^{5,10}$
David W. Latham,$^{12}$,
Allyson Bieryla,$^{12}$
Gilbert A. Esquerdo,$^{12}$ %\newauthor
and friends
\\
% List of institutions
$^{1}$Center for Cosmology and Particle Physics, Department of Physics, New York University, 726 Broadway, New York, NY 10003, USA\\
$^{2}$NASA Sagan Fellow\\
$^{3}$Oxford Astrophysics, Denys Wilkinson Building, University of Oxford, OX1 3RH, Oxford, UK\\
$^{4}$School of Physics and Astronomy, University of Birmingham, Birmingham B15 2TT, UK\\
$^{5}$Stellar Astrophysics Centre, Department of Physics and Astronomy, Aarhus University, Ny Munkegade 120, DK-8000 Aarhus C, Denmark\\
$^{6}$Department of Astronomy, The University of Texas at Austin, 2515 Speedway Boulevard, Austin, TX 78712, USA\\
$^{7}$Department of Astronomy, Columbia University, 550 W 120th St, New York, NY 10027, USA\\
$^{8}$Research School of Astronomy and Astrophysics, Mount Stromlo Observatory, The Australian National University, Canberra, ACT 2611, Australia\\
$^{9}$Institute for Astronomy, University of Hawai‘i, 2680 Woodlawn Drive, Honolulu, HI 96822, USA\\
$^{10}$Sydney Institute for Astronomy (SIfA), School of Physics, University of Sydney, NSW 2006, Australia\\
$^{11}$SETI Institute, 189 Bernardo Avenue, Mountain View, CA 94043, USA\\
$^{12}$Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138, USA
}

@@

A major outcome of the \kepler asteroseismology programme is a legacy sample of extremely well characterized stars that can serve as benchmarks for future work \citep{keplerlegacy1,keplerlegacy2}. As well as asteroseismology, by also using optical interferometry, it has been possible to determine fundamental parameters of main-sequence and giant stars with unprecedented precision \citep{huber12,thetacygwhite,white15}. Likewise by combining with spectroscopy, \citet{hawkinsapogee} have been able to produce a large sample of stars with precise elemental abundances by fitting spectroscopic data with \logg and \teff fixed to asteroseismically-determined values. It is necessary to calibrate such a study against benchmark stars with very precisely-determined parameters, which in practice requires nearby bright stars that are amenable to very high signal-to-noise spectroscopy plus asteroseismology \citep{creeveybenchmark}, parallaxes \citep{hawkinsbenchmarks}, and/or interferometry \citep{casagrandebenchmark,creeveybenchmark2}. This is especially important in the context of the \gaia mission \citep{gaia}, which has recently put out its second data release of 1,692,919,135 sources, including 1,331,909,727 with parallaxes \citep{gaiadr2}. These data will form the basis of many large surveys and it is vital that they are calibrated correctly. To this end, 34~FGK stars including both giants and dwarfs have been chosen as \gaia-ESO benchmark stars for which metallicities \citep{gaiabenchmark1}, effective temperatures and asteroseismic surface gravities \citep{gaiabenchmark3}, and relative abundances of $\alpha$ and iron-peak elements \citep{gaiabenchmark4} have been determined. This includes only four main sequence stars much cooler than the Sun, due to the paucity of such stars with asteroseismology. This has been accompanied by the release of high resolution spectra \citep{gaiabenchmark2} and formed the basis of extensions to lower metallicities \citep{gaiabenchmark5}, stellar twin studies \citep{gaiabenchmarktwins} and comparisons of stellar abundance determination pipelines \citep{gaiabenchmarkabundances}.

>>>>

% This author list is not final! If you think you should be in a different position please do not hesitate to say so.
\author[B. J. S. Pope et al.]{Benjamin J. S. Pope,$^{1,2,3}$\thanks{E-mail: benjamin.pope@nyu.edu}
Guy R. Davies,$^{4,5}$
Keith Hawkins,$^{6,7}$
Timothy R. White,$^{5,8}$\newauthor
Daniel Huber,$^{9,10,11}$
Ashley Chontos,$^{9}$
Victor Silva Aguirre,$^{5}$
Victoria Antoci,$^{5}$\newauthor
Suzanne Aigrain,$^{3}$ 
Timothy R. Bedding,$^{10,5}$
Jie Yu,$^{10,5}$ 
Amalie Stokholm,$^{5}$\newauthor
Timothy van Reeth,$^{5,10}$
David W. Latham,$^{12}$,
Allyson Bieryla,$^{12}$
Gilbert A. Esquerdo,$^{12}$\newauthor
and friends
\\
% List of institutions
$^{1}$Center for Cosmology and Particle Physics, Department of Physics, New York University, 726 Broadway, New York, NY 10003, USA\\
$^{2}$NASA Sagan Fellow\\
$^{3}$Oxford Astrophysics, Denys Wilkinson Building, University of Oxford, OX1 3RH, Oxford, UK\\
$^{4}$School of Physics and Astronomy, University of Birmingham, Birmingham B15 2TT, UK\\
$^{5}$Stellar Astrophysics Centre, Department of Physics and Astronomy, Aarhus University, Ny Munkegade 120, DK-8000 Aarhus C, Denmark\\
$^{6}$Department of Astronomy, The University of Texas at Austin, 2515 Speedway Boulevard, Austin, TX 78712, USA\\
$^{7}$Department of Astronomy, Columbia University, 550 W 120th St, New York, NY 10027, USA\\
$^{8}$Research School of Astronomy and Astrophysics, Mount Stromlo Observatory, The Australian National University, Canberra, ACT 2611, Australia\\
$^{9}$Institute for Astronomy, University of Hawai‘i, 2680 Woodlawn Drive, Honolulu, HI 96822, USA\\
$^{10}$Sydney Institute for Astronomy (SIfA), School of Physics, University of Sydney, NSW 2006, Australia\\
$^{11}$SETI Institute, 189 Bernardo Avenue, Mountain View, CA 94043, USA\\
$^{12}$Harvard-Smithsonian Center for Astrophysics, 60 Garden Street, Cambridge, MA 02138, USA
}

@@

A major outcome of the \kepler asteroseismology programme is a legacy sample of extremely well characterized stars that can serve as benchmarks for future work \citep{keplerlegacy1,keplerlegacy2}. In conjunction with spectroscopy, \citet{hawkinsapogee} have been able to produce a large sample of stars with precise elemental abundances by fitting spectroscopic data with \logg and \teff fixed to asteroseismically-determined values. It is necessary to calibrate such a study against benchmark stars with very precisely-determined parameters, which in practice requires nearby bright stars that are amenable to very high signal-to-noise spectroscopy plus asteroseismology \citep{creeveybenchmark}, parallaxes \citep{hawkinsbenchmarks}, and/or interferometry \citep{casagrandebenchmark,creeveybenchmark2}. This is especially important in the context of the \gaia mission \citep{gaia}, which has recently put out its second data release of 1,692,919,135 sources, including 1,331,909,727 with parallaxes \citep{gaiadr2}. These data will form the basis of many large surveys and it is vital that they are calibrated correctly. To this end, 34~FGK stars including both giants and dwarfs have been chosen as \gaia-ESO benchmark stars for which metallicities \citep{gaiabenchmark1}, effective temperatures and asteroseismic surface gravities \citep{gaiabenchmark3}, and relative abundances of $\alpha$ and iron-peak elements \citep{gaiabenchmark4} have been determined. This includes only four main sequence stars much cooler than the Sun, due to the paucity of such stars with asteroseismology. This has been accompanied by the release of high resolution spectra \citep{gaiabenchmark2} and formed the basis of extensions to lower metallicities \citep{gaiabenchmark5}, stellar twin studies \citep{gaiabenchmarktwins} and comparisons of stellar abundance determination pipelines \citep{gaiabenchmarkabundances}. Furthermore, by combining asteroseismology with optical interferometry, it has been possible to determine fundamental parameters of main-sequence and giant stars with unprecedented precision \citep{huber12,thetacygwhite,white15}.
